DATA 621 Homework #3

### 2019-10-30 hw3/HW3.Rmd
updated H3.rmd
Updated my model

density_models <- glm(target ~ nox_density +indus_density+age_density+dis_density+rad_density+tax_density+ptratio_density+lstat_density+medv_density, family = binomial(link = "logit"), train)
summary(density_models)
test$density_models <- ifelse(predict(density_models, test) < 0.5, 0, 1)
test$density_models_yhat <- predict(density_models, test)
confusionMatrix(factor(test$density_models), factor(test$target))
```

>>>>

density_models <- glm(target ~ nox_density +indus_density+age_density+dis_density+rad_density+tax_density+ptratio_density+lstat_density+medv_density+zn_density+rm_density+divider, family = binomial(link = "logit"), train)
summary(density_models)
test$density_models <- ifelse(predict(density_models, test) < mean(train$target), 0, 1)
test$density_models_yhat <- predict(density_models, test)
confusionMatrix(factor(test$density_models), factor(test$target))
```
